A quantitative framework for investigating the reliability of empirical network construction: supplemental information

### 2018-11-08 manuscript/reply_to_reviewers.tex

		\begin{refquote}
		Line 142.  But shouldn’t you model the probability of two species co-occurring?  The authors have a paper doing this…. Is that not a good idea?
		\end{refquote}

		\textbf{R:} Sure, this is an option in some cases, but we may not always have the information to do this. Co-occurrance modelling shouldn't be the only tool in the box.

		11. Issue of testing hypotheses based on inputs into models

		\begin{refquote}
		Line 121.  I think one of the reason non-Bayesians’ are not comfortable with the approach is that if you put in prior information on something like trait matching and test for trait matching and then discover trait matching is important – what does it mean?  Maybe this is too obvious (I realize there are tons of papers on how to choose priors) but I wonder if it is worth explaining (would a box or something be worthwhile?  I leave it up to the authors/editor)?  Maybe the issue could be acknowledged and an appropriate paper cited?
		\end{refquote}

		\textbf{R:} This question seems dumb. Do people actually do this?

		12. Redundancy in line 235

		\textbf{R:}

		13. System justification/description is odd.

		\begin{refquote}
		Line 240.  I found the justification for the system a bit odd.  Is the goal to show the gaps in sampling or to apply the model described thus far to consider the 3 different types of uncertainty outlined?  At this point the reader is confused about the goal… \\
		Line 249.  The statement about training data is redundant with what is stated above – adjust writing.
		\end{refquote}

		\textbf{R:}

		14. Unsure about the point of filtering networks

		\begin{refquote}
		Line 295 to 302.  I would think that this second step (i.e., filtered networks) is to explore sampling not to determine how networks will be influenced by uncertainty?  Do you need the filtering step to evaluate uncertainty (as written it seems that this is the case)?
		\end{refquote}

		15. Skepticism about sampling requirements to be sure interactions do not occur

		\begin{refquote}
		Line 361.  I find the statement that 30-50 individuals need to be evaluated a bit strong.  This statement is based on this study – are all systems like the gall system?  If species are specialized or bound to interact for some other reason (i.e., co-occurring when there are few other resources) wouldn’t you need to observe fewer individuals?  The point of the method is that you can estimate how many individuals are needed…. This is great!  But given that this can be estimated from any given system why give a value from one system and state that is what is required?  It defeats the point of the very nice method proposed…??
		\end{refquote}

		\textbf{R:} Of course, if you have extremely strong priors then you need less sampling. With a strong enough prior assumption that two species never interact, a researcher may feel justified not sampling at all (e.g., webs constructed based on "expert knowledge"). But if species shifting ranges are interesting/may be specialised because rare/information is not so available....

		\begin{refquote}
		I hope this review is helpful.  
		\end{refquote}

		\textbf{R:} We than the Reviewer for their literature suggestions and for demonstrating that our desire not to criticise hard-working empiricists could be misinterpreted as suggesting reduced sampling effort. We had not realised that anyone would consider such a possibility and have revised our manuscript to make it clearer that our approach is a complement to extensive sampling, not an excuse for poor sampling.

% -----------------------------------------------------------------------------
% -----------------------------------------------------------------------------
{\Large \bf Reply to Referee \#4}
% ---------------------------------------

	\begin{refquote}
	Comments to the Corresponding Author
	I have been surprised how little that sampling effects have been formally considered in the analysis of networks, so I welcome this contribution that provides a theoretical framework. Overall, I felt that this contribution was really helpful, and that it provides both a theoretical framework and a practical example.
	\end{refquote}

	\textbf{R:} [[Add end bit to this?]]

	1. Paper is poorly structured

	\begin{refquote}
	However, I felt that the structuring of the paper made it a challenge to understand and apply. It felt like the paper itself had been written in different sections (by different authors?) with not enough links between the sections. I also felt that there was a strong theoretical component, which is important, but there needed to be a stronger link with the issues around empirical ecology, as explained below.
	\end{refquote}

	\textbf{R:}

	2. Add more citations

	\begin{refquote}
	Introduction – T. Poisot and colleagues have done a lot of relevant work in this area, but I felt there was undue reference to their work in comparison with other relevant work. There were some obvious papers (e.g. sampling by Jordano, forbidden links by various others) that were not cited. A broader perspective on the literature would, I think, help the authors appreciate the value of their paper and the need to ensure that it is fully understandable and of practical use.
	\end{refquote}

	\textbf{R:} [[copy reply to R2]]

	3. Demand for praise of weighted metrics

	\begin{refquote}
	L36ff The authors should note the value of weighted metrics in taking account of sampling biases.
	\end{refquote}

	\textbf{R:} This is slightly confusing. How do weighted metrics account for sampling biases, exactly? Especially if species abundances are not assessed independently from interactions, it seems like weighted metrics would be more succeptable to sampling bias than unweighted metrics (as the weights will also be affected by differences in detectability). [[Is this acutally useful?]]

	4. Demand for extension to weigthed networks

	\begin{refquote}
	L45 It is a shame not to give some idea of how the method could be extended (or is this the intention of the authors?). For empirical analysis of networks it is rare to use binary networks given the value of weighted networks for taking account of sampling biases. Indeed, I am much less concerned about whether an interaction never occurs, and much more concerned with the frequency of occurrence.
	\end{refquote}

@@

	\begin{refquote}
	L45 It is a shame not to give some idea of how the method could be extended (or is this the intention of the authors?). For empirical analysis of networks it is rare to use binary networks given the value of weighted networks for taking account of sampling biases. Indeed, I am much less concerned about whether an interaction never occurs, and much more concerned with the frequency of occurrence.
	\end{refquote}

	\textbf{R:} Unfortunately, the use of binary networks is not as rare as the Reviewer thinks, particularly in food webs where it is often difficult to quantify interaction strengths or frequencies in the field. We absolutely agree that weighted networks are much more valuable when they are available but did not wish to exclude those without such data. [[Do we want to add a bit of non-binary stuff or just make it clearer that we are talking about feasibility and that probabilities of occurrance could be layered on later?]]

	5. The one valuable section is poorly-integrated with the rest of the paper.

	\begin{refquote}
	L50 This is a nice and clearly explained description of the problem that many network ecologists ignore, or are unaware of.
	Section from L50. This section is valuable, but had very weak links with the empirical analysis later in the paper. For instance in the example of the gall-formers, there was not formal discussion about the different sources of uncertainty. [[So we need to state more clearly that we cannot distinguish these after the fact.]]
	\end{refquote}

	\textbf{R:}

	6. Process uncertainty poorly defined, many quibbles about sampling

	\begin{refquote}
	L76ff ‘Process uncertainty’ is not defined. The simplistic example of interaction uncertainty (fish eating a cactus) does not help the reader understand the detail of what is meant by ‘interaction uncertainty’. The two examples of ‘local constraints’ (weather and habitat) are operating on completely different temporal scales (note – it is defined differently in L109). I would regard the issue of weather as much closer to detection uncertainty (e.g. for a pollinator, it would be likely to be interacting if the weather was better), whereas the issue of habitat is closer to the authors’ ‘interaction uncertainty’ (the species don’t interact because they are not, or never, co-occurring in a habitat). Also if the species occur in different habitats then with an appropriate spatial scale of sampling then they do not co-occur – so the issue seems redundant. [[I suspect that the authors are thinking of a meta- or master network in much of their study, but this is not clear (or I have misunderstood and it needs to be explained better), i.e. the predicted presence of an interaction is not the presence of an interaction at the local site (taking detection and process uncertainty into account) but the ability to assess ‘interaction uncertainty’.]][[This is a bit separate from their issue]]
	\end{refquote}

@@

		\begin{quotation}

		Expanding sampling to cover a broader spatial or temporal range (e.g., sampling in a variety of microhabitats or during a variety of weather conditions) will also help to reduce process uncertainty if resource constraints permit.

		\end{quotation}

	7. Point about temporal scales of interaction

	\begin{refquote}
	L76ff Different interactions occur at different temporal scales, so it is important to consider where the role of this study lies. For instance, a pollinator-flower interaction is quick (and even the evidence of it, e.g. pollen on the insect, is not long-lasting) whereas an active gall-former interaction could be present for a couple of months and could be detected for even longer (on senescing leaves).
	\end{refquote}

@@

		\begin{quotation}

			Some types of interactions will have higher detection uncertainty than others (e.g., pollination or predation often take place very quickly while parasitism can last for months or years). Even long-term interactions, however, can be missed, especially if species are difficult to identify or if not all individuals of a species share the interaction. Parasites, for example, are often concentrated in only a few individuals~\citep{Lagrue2017}. If these infected individuals do not happen to be included in a sample, their interactoins will be missed.

		\end{quotation}

	8. Confusion about goal of modelling

	\begin{refquote}
	I was struggling to really understand what the authors were really trying to model (partly because of the lack of a link between the theoretical and empirical parts of the paper). Are the authors trying to estimate L (the probability that an interaction is feasible or not – I would describe this as a ‘master’ or meta- network), or is it that they are trying to estimate X|L (the probability that the interaction locally occurs)? I would be interested in both, but the second aspect seemed to be ignored in the gall-former example.
	\end{refquote}

	\textbf{R:}

	9. ??

	\begin{refquote}
	L136 This is a completely different issue, that you do not address in the paper.
	\end{refquote}

	\textbf{R:}

	10. Explain Bayesian approach more simply

	\begin{refquote}
	L147 Your Bayesian approach seems important, especially the prior information, and I would have appreciated it being explained more simply.
	\end{refquote}

	\textbf{R:} This comment conflicts with Reviewer 1's request that we remove much of our early description of the Bayesian framework on the grounds that it is easy to Google. As one way to address both comments, we have revised the manuscript to more clearly position our analysis of the willow-galler network as a worked example. We hope that the Reviewer will find it easier to understand our framework by following along with an example than would be the case if we expanded our abstract discussion.

	11. Integrate L155ff with previous section

	\begin{refquote}
	L155ff I think it would be helpful for this section to be integrated with the previous section. It relies on the reader putting quite a lot of work in to understand the link between the two.
	\end{refquote}

	\textbf{R:}

	12. Ideas presented in L209, L262, L310 are important but explained too briefly

	\begin{refquote}
	L209ff This seems a really important set of ideas, but they are exemplified very briefly and very simplistically in the paper (L262, L310). I would have appreciated a much clearer explanation and example.
	\end{refquote}

	\textbf{R:}

	13. Reframe line 241 in terms of solutions rather than difficulties

	\begin{refquote}
	L241 I wonder if you could phrase this more positively as ‘solutions’ rather than just ‘difficulties’?
	\end{refquote}

	\textbf{R:}

	14. Line 283 is unclear

@@

	L283 This seems a very important point and should be explained/expanded more clearly.

	\textbf{R:}

	15. Line 291: does assuming probability of 1 for observed interactions introduce bias?

	\begin{refquote}
	L291 I have wondered about this – does assuming a probability of 1 for observed interactions create a bias? The observed interactions are a stochastic set of the possible interactions, so by treating observed interactions as 1 and other (equally likely?) unobserved interactions as <1 will surely bias the network metrics. I’m not sure of the solution and would welcome thoughts on this in the paper.
	\end{refquote}

	16. Filtering seems arbitrary

	\begin{refquote}
	L298 These seem arbitrary. It is not clear what is filtered, or its justification – is it the unique interactions, unique interaction per site or samples? How do these compare to typical sampling effort?
	\end{refquote}

	\textbf{R:} The filtering threshold were arbitrary and intended solely to demonstrate how decreasing detection probability might shape the network actually collected in the field. We had believed that our example network was extremely well-sampled and therefore clustered filtering thesholds closer to p(detection)=1; as it appears that even this very intesively sampled network did not detect many interactions we have changed to a broader and more even set of filtering thresholds. We have also revised this section to make it clear what is being filtered [[to do]].\\
	Unfortunately, we do cannot compare our filtered networks to many published networks as detection probabilities are not often estimated or reported. We do note, however, that Bascompte (2013) also reports quite low proportions of detected interactions ([[exact #]]). This suggests that the low detection probabilities we infer are not unique to our study. We have added a note comparing our results with Bascompte's [[to do]] and an explicit call for future researchers to report estimates of their detection probabilities [[to do]].

	17. Expand discussion of results on line 321

	\begin{refquote}
	L321 This is a really important and interesting set of results that are worthy of greater discussion. The issue of metrics from sampled networks is important, but gets lost in the paper. Please expand upon this.
	\end{refquote}

	\textbf{R:}

	18. As a review, the manuscript is disappointing.

	\begin{refquote}
	Overall, I fear that this review is rather meandering, but I think that reflects some of the challenges I have with the paper. Currently I do not think the paper would be used by empirical network ecologists because they either would not understand its relevance or would not be able to apply it practically. This would be a great shame. I hope that the comments are clear enough to allow the authors to improve the paper – the paper has the potential to be important and very useful.
	\end{refquote}

	\textbf{R:} As we did not intend to write a review, we understand the Reviewer's complaint. This shows that we did not clearly establish the purpose of our manuscript, and we hope that our revision corrects this. In particular, we hope that we have established the relevance of our method and offered enough of an explanation that empiricists will be able to apply it. Our goal is to increase access to a statistical technique which we see as complementary to high-quality field work, and we believe that the Reviewer's comments will help us to achieve this.

\clearpage

\end{document}

### 2018-11-22 manuscript/reply_to_reviewers.tex

	\end{refquote}

	\textbf{R:} We appreciate the thoughtful feedback by the four referees. We take particular note of the comments regarding the structure and grounding of our introduction and have worked to address this. Reviewer 2's comments take a different view of the purpose and scope of the manuscript than the other reviewers; we respect their ideas but feel that some are beyond the scope of the present manuscript. In particular, we do not feel that a full simulation study is necessary given the simplicity of our framework. We emphasize that we are not introducing a software package (although we do provide simple code to aid those who are new to the field), nor are we introducing an entirely new framework (as the other Reviewers point out, many components of our approach have been touched on by previous work). The novelty and impact of our work lies in connecting a Bayesian statistical approach to the problem of limited and uneven sampling (driven by difference in species abundances, detectabilities, constrained time and budgets, etc.) and, we hope, in making this method more accessable to those without extensive statistical or modelling experience. Because of the difference between Reviewer 2 and the other Reviewers, we have opted to prioritise the majority view and focused first on comments by Reviewers 1, 3, and 4. We hope that, in the course of these revisions, we have at least partially adressed Reviewer 2's concertns as well.

\newpage

% ----------------------------------------------------------------------
% ----------------------------------------------------------------------
{\Large \bf Reply to Reviewer \#1}
% ---------------------------------------

	1. Suggestion to refocus on prior selection [[not done]]

@@

		\textbf{R:} We thank the Reviewer for the suggestion to expand our discussion of prior selection, particularly with regard to approxmimate/empirical bayes. [[Expand refs to this]] We now walk through flat, informed, and empirical priors as suggested (lines XX-XX) and refer to the controversy surrounding empirical priors in our discussion (lines XX-XX).\\
		We also appreciate the Reviewer's comments on our introduction. We feel that understanding the problem of uncertain detection of interactions is important motivation for a reader not already familiar with Bayesian procedures to wade through a larger discussion on priors. Therefore we have revised and, hopefully, streamlined our discussion but do not jump straight in to priors. We have, however, taken care to introduce our analysis as a worked example (lines XX-XX) and hope that this helps to reduce the conflict between the introduction and our data. [[Add something else about different priors? Add different priors to our analyses?]]
		[[Definitely should expand this, but do we want to really focus on those?]][[not quite done]]

	2. Suggestion to add more literature [[in progress]]

@@

		\begin{refquote}
		The introduction flows well and is thoughtfully laid out. Given the enormous amount of literature in the field, it is not possible to provide a full set of citations. However, it seems remiss to not consider Jordano (2016) in the sampling section.
		\end{refquote}

		\textbf{R:} We thank the Reviewer for their compliments to our introduction and for the recommendation of Jordano 2016. We have incorporated this reference as suggested. Following comments from other reviewers, we have refined and slightly restructured our introduction in the hope of more clearly establishing the goal of our manuscript ('narrowing our net'). We hope that this revised introduction will also meet with the Reviewer's approval. [[done]]

	3. Suggestion to de-emphasize MLE estimate and get straight to Bayes [[done]]

@@

		\begin{refquote}
		It’s a bit confusing to lead the reader towards a Bayesian analysis, and then immediately start with the MLE estimate. Why is this needed at all? (L162-186). Just start at 187?
		\end{refquote}

		\textbf{R:} The section on the MLE estimate was designed to illustrate the large sample sizes needed in the absence of a Bayesian framework. Upon reflection, we see have moved this demonstration to a box dealing specifically with sampling. We now begin with the Bayesian beta distribution as suggested. [[I think done?]]

	4. Suggestion to remove moments of the beta distribution [[done]]

@@

		\begin{refquote}
		I think a bit of space is wasted on defining the moments of the beta distribution. This is very googleable, and almost too thorough. I think the space is better utilized aligning the ecological challenge and the quantitative method.
		\end{refquote}

		\textbf{R:} While we feel that a short introduction to the beta distribution is important to bring researchers new to Bayesian statistics up to speed (and give them some keywords to Google), we accept the Reviewer's suggestion to reduce the amount of space given to the beta. We have therefore moved the description of basic properties to Appendix S2. The remaining paragraph introducing the beta distribution now leads directly into the section describing prior selection.

	5. Novelty of the study not clear in current framing [[not done? Done? Clearer?]]

		\begin{refquote}
		I’m wrestling with the novelty of the work as presented and whether it reaches the standard for publication at MEE. Certainly, much of this logic is laid out in other works. The authors are well aware of this and have made significant contributions to this topic in the last few years. In particular, the authors should try to be much more explicit about the contribution they hope to offer that hasn’t been covered. ...
		While it is true that none of the [suggested] papers do the exact same thing as this manuscript, they all	orbit the same topic. 
		\end{refquote}

@@

		\textbf{R:} We thank the Reviewer for the literature suggestions and now include them in our introduction and/or discussion. We emphasize the board applicability of our appraoch across network types and where species traits affecting interaction probability may not be known. [[Make sure this comes through]] We hope that the contribution our manuscript makes is now clearer.

	6. Potential contradiction [[done]]

		\begin{refquote}
		L89 for example, seems to conflict with the two paragraphs immediately following it?
		\end{refquote}

		\textbf{R:} We have now address questions relating to sampling in a dedicated box. We hope that the revisions make our stance on repeated sampling clearer and that there are no longer apparent contradictions.

	7. Final comment on framing the study [[I think done?]]

@@

		\textbf{R:} We thank the Reviewer for their compliments and accept their suggestion that we are somewhat overexcited about our approach. We have refined the introduction to be more specific about the problem we are attempting to solve. We have also expanded our treatment of prior selection and hope that our paper now reads as achieving its goal.

	% 	Literature suggestions:
		% Jordano, P. (2016). Sampling networks of ecological interactions. Functional Ecology, 30(12), 1883–1893. doi:10.1111/1365-2435.12763
		% Bartomeus, I. (2013). Understanding Linkage Rules in Plant-Pollinator Networks by Using Hierarchical Models That Incorporate Pollinator Detectability and Plant Traits. PLoS ONE, 8(7), 1–9. doi:10.1371/journal.pone.0069200
		% Poisot, T., Cirtwill, A. R., Cazelles, K., Gravel, D., Fortin, M.-J., & Stouffer, D. B. (2016). The structure of probabilistic networks. Methods in Ecology and Evolution, 7(3), 303–312. doi:10.1111/2041-210X.12468
		% Poisot, T., Stouffer, D. B., & Gravel, D. (2015). Beyond species: why ecological interaction networks vary through space and time. Oikos, 124(3), 243–251. doi:10.1111/oik.01719
		% Graham, C. H., & Weinstein, B. G. (2018). Towards a predictive model of species interaction beta diversity. Ecology Letters. doi:10.1111/ele.13084
		% Gravel, D., Poisot, T., Albouy, C., Velez, L., & Mouillot, D. (2013). Inferring food web structure from predator-prey body size relationships. Methods in Ecology and Evolution, 4(11), 1083–1090. doi:10.1111/2041-210X.12103
		% Wells, K., & O’Hara, R. B. (2013). Species interactions: Estimating per-individual interaction strength and covariates before simplifying data into per-species ecological networks. Methods in Ecology and Evolution, 4(1), 1–8. doi:10.1111/j.2041-210x.2012.00249.x

% ----------------------------------------------------------------------
% ---------------------------------------------------------------------
{\Large \bf Reply to Referee \#2}
% ---------------------------------------

@@

	\end{refquote}

	Minor points:

	-l.62: define formally T
	-l.244: this is weird to mention that the analysis has been done on another dataset but that the results will not be discussed… What is the interest for the reader?
	-l.149: since the authors consider the interactions are independent, there is morally no network in the approach (except the result)
	-l.252: not clear. Why this choice?
	-l.259: not clear
	-l.278: the authors investigate the consequence of uncertainity on network metrics. This question is of peculiar interest, but here it is restricted to the connectance and nestedness. Why these two metrics? Why not others? What is the impact of integrating incertainity into the metrics computation? (we guess the answers but we could expect the authors develop these points).
	l.291: explain better the simulation procedure
	l.306: given the shape of the distribution (exponential), the mean is not an appropriate indicator.
	l.327: what does it mean? How is it possible?

% ----------------------------------------------------------------------
% ----------------------------------------------------------------------
{\Large \bf Reply to Referee \#3}
% ---------------------------------------

	\begin{refquote}
		Comments to the Corresponding Author
		Overall, I think this is a very good paper and makes an important contribution.  I think there are three main ways it can be improved: 1.      The simplest – do a better job of acknowledging what else has been done in the field – much of which has actually been done by the authors and their collaborators. ... 2.      Provide more clarity in descriptions making sure to consider how terms and ideas have been used previously. ... 3.      The set up (introduction) to the case study is quite odd and somehow seems off topic – or at least not logical based on what the reader has read up to that point.
		I hope this review is helpful.  
		\end{refquote}

	1. Add more references to the literature [[in progress]]

@@

	3. Introduction of the case study seems off-topic and illogical. [[not done - R1 also points out that this is a weak point]]

		\begin{refquote}
		3.      The set up (introduction) to the case study is quite odd and somehow seems off topic – or at least not logical based on what the reader has read up to that point.
		\end{refquote}

		\textbf{R:}

	4. Misunderstanding of our point about sampling effort [[maybe done? in progress]]

@@

			\end{quotation}

	7. Why not always model probabilities of co-occurrance? [[done]]

		\begin{refquote}
		Line 142.  But shouldn’t you model the probability of two species co-occurring?  The authors have a paper doing this…. Is that not a good idea?
		\end{refquote}

		\textbf{R:} Of course modelling the probability of co-occurrence is an option for many systems (e.g., aquatic food webs where ranges of fish species are fairly well-known, as in~\citet{Gravel2013}). In some systems, however, the factors affecting probabilities of co-occurrence may not be known. We therefore cannot suggest modelling co-occurrence as a panacea. Instead, we now emphasize that co-occurrence probabilities are one thing that could be included in a prior (lines XX-XX - section Informative priors). 
		\smallskip
		The fact remains that a lack of observed interactions between species which do not co-occur tells us nothing about whether these species \emph{could} interact if they should begin to co-occur (e.g., following a range shift). Following the Revewier's suggestion, we have revised our manuscript to clarify our technology. In particular, we have taken care to specify which level of uncertainty we are addressing at different points in the manuscript. We hope that this will remove some of the confusion about whether or not modelling different components of uncertainty/sampling more is a good idea.

	8. Issue of testing hypotheses based on inputs into models [[done]]

@@

		\begin{refquote}
		Line 121.  I think one of the reason non-Bayesians’ are not comfortable with the approach is that if you put in prior information on something like trait matching and test for trait matching and then discover trait matching is important – what does it mean?  Maybe this is too obvious (I realize there are tons of papers on how to choose priors) but I wonder if it is worth explaining (would a box or something be worthwhile?  I leave it up to the authors/editor)?  Maybe the issue could be acknowledged and an appropriate paper cited?
		\end{refquote}

		\textbf{R:} Following suggestions by this Reviewer and another, we have substantially expanded our discussion of different options for priors (including the trait-based and co-occurrence models the Reviewer points out). It seems fairly obvious that discovering that trait-matching is important in a model framework which relies of trait-matching as a starting assumption does not mean very much... but we also recognize that researchers unfamiliar with Bayesian approaches might prioritize reducing uncertainty and therefore include all available information even when it conflicts with the study question. We have therefore added an explicit statement that researchers wishing to test the influence of a particular trait (for example) should \emph{not} include that trait in their prior (lines XX-XX). We hope that this statement, and the expanded discussion of different types of priors more generally, allay the Reviewer's concerns.

		\begin{quotation}
			Similarly, if detailed information is available but refers to the question at hand, it is best to use a less informative prior so as not to force a particular result. For example, if researchers are interested in testing whether body-size ratios affect probabilities of interaction they should not use a prior which predicts interactions based on body sizes.
		\end{quotation}

	9. Redundancy in line 235 [[done]]

		\textbf{R:} The redundant line has been removed. Thank you for pointing this out.

	10. Unsure about the point of filtering networks [[not done]]

@@

		\begin{refquote}
		Line 295 to 302.  I would think that this second step (i.e., filtered networks) is to explore sampling not to determine how networks will be influenced by uncertainty?  Do you need the filtering step to evaluate uncertainty (as written it seems that this is the case)?
		\end{refquote}

		\textbf{R:}

	11. Skepticism about sampling requirements to be sure interactions do not occur [[done]]

@@

		\begin{refquote}
		Line 361.  I find the statement that 30-50 individuals need to be evaluated a bit strong.  This statement is based on this study – are all systems like the gall system?  If species are specialized or bound to interact for some other reason (i.e., co-occurring when there are few other resources) wouldn’t you need to observe fewer individuals?  The point of the method is that you can estimate how many individuals are needed…. This is great!  But given that this can be estimated from any given system why give a value from one system and state that is what is required?  It defeats the point of the very nice method proposed…??
		\end{refquote}

		\textbf{R:} The point of our method is not actually to quantify the amount of sampling needed. Although the ideal sampling effort \emph{can} be calculated using the framework we put forward (as we demonstrate), the real point is to quantify how uncertain we are that an interaction we do not observe really does not occur. Given this, we do not think that recommending uncertainty be explicitly stated undermines our point at all. 
		\smallskip
		The Reviewer's suggestion that we might need fewer samples for species that are "specialized or bound to interact for some other reason" reflects a very strong prior. In this case, yes we would need fewer samples for the species concerned. With sufficiently strong priors, it is not necessary to sample at all! For example, in most food webs it is assumed that basal resources will never consume prey even if a given resource and a given animal are never observed co-occurring and it is generally accepted that there is very low uncertainty about these zeros. In many cases, the assumptions involved in excluding interactions are less clear-cut and different researchers may disagree about which species are "bound to interact" (or not to interact). The concept of pollination syndromes is one example - many flower visitors are less rigidly specialized on particular flower types than initially thought~\citep{}. To address such "forbidden links", we now suggest that researchers explicitly state both the uncertainty about data-based zeros and the assumptions by which they create structural zeros. This will allow future researchers to evaluate the uncertainty about all interactions in a network as the state of expert knowledge changes. We hope that this expanded recommendation (lines XX-XX) is clearer.

			Second, researchers should acknowledge the varying levels of confidence surrounding interactions between species pairs. In the absence of strong prior information a very high level of sampling (i.e., 30-50 observations in our example) is needed \emph{for each species pair}. This is not likely to be possible for most studies. including the $n$ and $k$ values for each interaction will clearly indicate which unobserved interactions are most likely to be observed with further sampling and which estimates are more reliable. Where there are strong prior expectations about pairs of species that will not interact, these should be explicitly stated so that readers know which zeros in an interaction matrix are based on observed data and which are based primarily upon expert knowledge.

@@

			Second, researchers should acknowledge the varying levels of confidence surrounding interactions between species pairs. In the absence of strong prior information a very high level of sampling (i.e., 30-50 observations in our example) is needed \emph{for each species pair}. This is not likely to be possible for most studies. including the $n$ and $k$ values for each interaction will clearly indicate which unobserved interactions are most likely to be observed with further sampling and which estimates are more reliable. Where there are strong prior expectations about pairs of species that will not interact, these should be explicitly stated so that readers know which zeros in an interaction matrix are based on observed data and which are based primarily upon expert knowledge.

		\end{quotation}

\newpage

% ----------------------------------------------------------------------
% ----------------------------------------------------------------------
{\Large \bf Reply to Referee \#4}
% ---------------------------------------

	\begin{refquote}
		Comments to the Corresponding Author
		I have been surprised how little that sampling effects have been formally considered in the analysis of networks, so I welcome this contribution that provides a theoretical framework. Overall, I felt that this contribution was really helpful, and that it provides both a theoretical framework and a practical example.

		Overall, I fear that this review is rather meandering, but I think that reflects some of the challenges I have with the paper. Currently I do not think the paper would be used by empirical network ecologists because they either would not understand its relevance or would not be able to apply it practically. This would be a great shame. I hope that the comments are clear enough to allow the authors to improve the paper – the paper has the potential to be important and very useful.
		\end{refquote}

	1. Paper is poorly structured [[not done]]

@@

		\textbf{R:}

	2. Add more citations [[done]]

		\begin{refquote}
		Introduction – T. Poisot and colleagues have done a lot of relevant work in this area, but I felt there was undue reference to their work in comparison with other relevant work. There were some obvious papers (e.g. sampling by Jordano, forbidden links by various others) that were not cited. A broader perspective on the literature would, I think, help the authors appreciate the value of their paper and the need to ensure that it is fully understandable and of practical use.
		\end{refquote}

		\textbf{R:} We have cited addition literature as recommended by Reviewer 1, including a paper by Jordano. If the Reviewer has any suggestions of specific papers that they feel are missing, we would be happy to consider them as well. Note, however, that we do not intend our manuscript to be a complete review of the literature surrounding interaction probabilities. We hope that the citations we have added appear more balanced to the Reviewer.

	3. Demand for praise of weighted metrics [[not done]]

@@

	5. The one valuable section is poorly-integrated with the rest of the paper. [[not done]]

		\begin{refquote}
		L50 This is a nice and clearly explained description of the problem that many network ecologists ignore, or are unaware of.
		Section from L50. This section is valuable, but had very weak links with the empirical analysis later in the paper. For instance in the example of the gall-formers, there was not formal discussion about the different sources of uncertainty. [[So we need to state more clearly that we cannot distinguish these after the fact.]]
		\end{refquote}

		\textbf{R:}

	6. Process uncertainty poorly defined, many quibbles about sampling [[done?]]

@@

	11. Integrate L155ff with previous section [[not done]]

		\begin{refquote}
		L155ff I think it would be helpful for this section to be integrated with the previous section. It relies on the reader putting quite a lot of work in to understand the link between the two.
		\end{refquote}

		\textbf{R:}

	12. Ideas presented in L209, L262, L310 are important but explained too briefly [[not done]]

@@

		\begin{refquote}
		L209ff This seems a really important set of ideas, but they are exemplified very briefly and very simplistically in the paper (L262, L310). I would have appreciated a much clearer explanation and example.
		\end{refquote}

		\textbf{R:}

	13. Reframe line 241 in terms of solutions rather than difficulties [[not done]]

@@

		\begin{refquote}
		L241 I wonder if you could phrase this more positively as ‘solutions’ rather than just ‘difficulties’?
		\end{refquote}

		\textbf{R:}

	14. Line 283 seems to be a very important point and should be explained more clearly [[not done]]
